### 2021-09-20 paper/localpsf.tex
move Sij=Fi(xj) into lemma

We may efficiently solve optimization problem \eqref{eq:wi_optimization_problem_generic} via the following procedure:
\begin{enumerate}
	\item For each sample point $x_i$, we compute a function $\firstgreens_i$ by solving the following Neumann Poisson problem:
	\begin{equation}
		\label{eq:psi_eq}
		\begin{cases}
			\Delta \firstgreens_i = \delta_{x_i} - 1/|\Omega|, & \text{in }\Omega, \\
			\nu \cdot \nabla \firstgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \firstgreens_i(x) dx = 0$. Here $\delta_{x_i}$ is the point source centered at $x_i$, $|\Omega|$ is the measure of the domain $\Omega$, and $\nu$ is the normal vector to $\partial \Omega$.
	\item For each function $\firstgreens_i$, we compute a function $\secondgreens_i$ by solving another Neumann Poisson problem:
	\begin{equation}
		\label{eq:theta_eq}
		\begin{cases}
			\Delta \secondgreens_i = \firstgreens_i, & \text{in }\Omega, \\
			\nu \cdot \nabla \secondgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \secondgreens_i(x) dx = 0$.
	\item The solution to optimization problem \eqref{eq:wi_optimization_problem_generic}, which we denote by $v_*$, is formed as follows:
	\begin{equation}
		\label{eq:optimal_v}
		v_*(x) := \constcoeff + \sum_{i=1}^\convrank \secondgreenscoeff_i \secondgreens_i(x),
	\end{equation}
	where the constants $\secondgreenscoeff_i \in \mathbb{R}$, $i=1,\dots,\convrank$, and $\constcoeff \in \mathbb{R}$ are the solution to the following linear system:
	\begin{equation}
		\label{eq:interpolation_linear_system}
		\begin{bmatrix}
			\pointinteractionmatrix & \bm{1} \\ \bm{1}^T & 0
		\end{bmatrix}
		\begin{bmatrix}
			\bm{\secondgreenscoeff} \\ \constcoeff
		\end{bmatrix}
		=
		\begin{bmatrix}
			\bm{\interpolatedvalues} \\ 0
		\end{bmatrix}.
	\end{equation}
	Here $\bm{\secondgreenscoeff} \in \mathbb{R}^\convrank$ is the vector with $i$th component $\secondgreenscoeff_i$, $\bm{1} \in \bm{R}^\convrank$ is the column vector of all ones, $\bm{\interpolatedvalues} \in \mathbb{R}^\convrank$ is the vector with $i$th component $\interpolatedvalues_i$, and $\pointinteractionmatrix \in \mathbb{R}^{\convrank \times \convrank}$ is the matrix with entries given by
	\begin{equation}
		\label{eq:S_matrix}
		\pointinteractionmatrix_{ij} := \left( \firstgreens_i, \firstgreens_j \right)_{L^2(\Omega)}.
	\end{equation}
\end{enumerate}
Linear system \eqref{eq:interpolation_linear_system} is the KKT system that arises if one solves optimization problem \eqref{eq:wi_optimization_problem_generic} on the $\convrank+1$-dimensional subspace of $H^2_N(\Omega)$ spanned by the functions $\secondgreens_i$, $i=1,\dots,\convrank$, and the constant function $C(x)=1$. In Theorem \ref{thm:wi_no_breakdown}, we prove that this procedure does not break down, and in Theorem \ref{thm:wi_alg_is_correct}, we prove that the function $v_*$ produced by this procedure is the solution to optimization problem \eqref{eq:wi_optimization_problem_generic} on $H^2_N(\Omega)$.

@@

\begin{lem}[Preparation for Theorem \ref{thm:wi_alg_is_correct}]
	\label{lem:psi_delta_eval}
	We have
	\begin{equation}
		\label{eq:inline_wi_lemma}
		h(x_j) = \left(\firstgreens_j, \Delta h\right)_{L^2(\Omega)} + \avg(h)
	\end{equation}
	for all $h\in H^2_N(\Omega)$, where
	\begin{equation*}
		\avg(h) :=	 \frac{1}{|\Omega|} \int_\Omega h ~dx,
	\end{equation*}
	and $|\Omega| = \int_\Omega 1 ~dx$ is the Lebesgue measure of $\Omega$.
\end{lem}

@@

@@

	\paragraph{Feasibility} To show that $v_*$ is feasible (i.e., $v_* \in X$), we must show that $v_*(x_i) = \interpolatedvalues_i$ for $i=1,\dots,\convrank$. We have
	\begin{align*}
		v_*(x_i) &= \constcoeff + \sum_{j=1}^\convrank \secondgreenscoeff_j \secondgreens_j(x_i) \\
		&= \constcoeff + \sum_{j=1}^\convrank \secondgreenscoeff_j \left(\firstgreens_i, \Delta \secondgreens_j\right)_{L^2(\Omega)} + \avg\left(\secondgreens_j\right) \\
		&= \constcoeff + \sum_{j=1}^\convrank \secondgreenscoeff_j \left(\firstgreens_i, \firstgreens_j\right)_{L^2(\Omega)} \\
		&= \constcoeff + \sum_{j=1}^\convrank \secondgreenscoeff_j \pointinteractionmatrix_{ij}
	\end{align*}
	In the first line we used the definition of $v_*$ in \eqref{eq:optimal_v}. In the second line we used Lemma \ref{lem:psi_delta_eval}. In the third line we used the facts that, by construction, $\Delta \secondgreens_j = \firstgreens_j$ and $\int_\Omega \secondgreens_j(x) dx = 0$. In the fourth line we used the definition of $\pointinteractionmatrix$ in \eqref{eq:S_matrix}. Hence the condition $v_*(x_i) = \interpolatedvalues_i$ for $i=1,\dots,\convrank$ may be written in matrix form as
	\begin{equation*}
		\pointinteractionmatrix \bm{\secondgreenscoeff} + \constcoeff \bm{1} = \bm{\interpolatedvalues},
	\end{equation*}
	and this must hold because it is the first block row of system \eqref{eq:interpolation_linear_system} which is solved to compute $\bm{\secondgreenscoeff}$ and $\constcoeff$. So $v_* \in X$.

>>>>

The solution to optimization problem \eqref{eq:wi_optimization_problem_generic} is given via the following procedure:
\begin{enumerate}
	\item For each sample point $x_i$, we compute a function $\firstgreens_i$ by solving the following Neumann Poisson problem:
	\begin{equation}
		\label{eq:psi_eq}
		\begin{cases}
			\Delta \firstgreens_i = \delta_{x_i} - 1/|\Omega|, & \text{in }\Omega, \\
			\nu \cdot \nabla \firstgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \firstgreens_i(x) dx = 0$. Here $\delta_{x_i}$ is the point source centered at $x_i$, $|\Omega|$ is the measure of the domain $\Omega$, and $\nu$ is the normal vector to $\partial \Omega$.
	\item For each function $\firstgreens_i$, we compute a function $\secondgreens_i$ by solving another Neumann Poisson problem:
	\begin{equation}
		\label{eq:theta_eq}
		\begin{cases}
			\Delta \secondgreens_i = \firstgreens_i, & \text{in }\Omega, \\
			\nu \cdot \nabla \secondgreens_i = 0 & \text{on } \partial \Omega,
		\end{cases}
	\end{equation}
	with condition $\int_\Omega \secondgreens_i(x) dx = 0$.
	\item The solution to optimization problem \eqref{eq:wi_optimization_problem_generic}, which we denote by $v_*$, is formed as follows:
	\begin{equation}
		\label{eq:optimal_v}
		v_*(x) := \constcoeff + \sum_{i=1}^\convrank \secondgreenscoeff_i \secondgreens_i(x),
	\end{equation}
	where the constants $\secondgreenscoeff_i \in \mathbb{R}$, $i=1,\dots,\convrank$, and $\constcoeff \in \mathbb{R}$ are the solution to the following linear system:
	\begin{equation}
		\label{eq:interpolation_linear_system}
		\begin{bmatrix}
			\pointinteractionmatrix & \bm{1} \\ \bm{1}^T & 0
		\end{bmatrix}
		\begin{bmatrix}
			\bm{\secondgreenscoeff} \\ \constcoeff
		\end{bmatrix}
		=
		\begin{bmatrix}
			\bm{\interpolatedvalues} \\ 0
		\end{bmatrix}.
	\end{equation}
	Here $\bm{\secondgreenscoeff} \in \mathbb{R}^\convrank$ is the vector with $i$th component $\secondgreenscoeff_i$, $\bm{1} \in \bm{R}^\convrank$ is the column vector of all ones, $\bm{\interpolatedvalues} \in \mathbb{R}^\convrank$ is the vector with $i$th component $\interpolatedvalues_i$, and $\pointinteractionmatrix \in \mathbb{R}^{\convrank \times \convrank}$ is the matrix with entries given by
	\begin{equation}
		\label{eq:S_matrix}
		\pointinteractionmatrix_{ij} := \left( \firstgreens_i, \firstgreens_j \right)_{L^2(\Omega)}.
	\end{equation}
\end{enumerate}
Linear system \eqref{eq:interpolation_linear_system} is the KKT system that arises if one solves optimization problem \eqref{eq:wi_optimization_problem_generic} on the $\convrank+1$-dimensional subspace of $H^2_N(\Omega)$ spanned by the functions $\secondgreens_i$, $i=1,\dots,\convrank$, and the constant function $C(x)=1$. In Theorem \ref{thm:wi_no_breakdown}, we prove that this procedure does not break down, and in Theorem \ref{thm:wi_alg_is_correct}, we prove that the function $v_*$ produced by this procedure is the solution to optimization problem \eqref{eq:wi_optimization_problem_generic} on $H^2_N(\Omega)$.

@@

\begin{lem}[Integral representation of delta distribution on $H^2_N(\Omega)$]
	\label{lem:psi_delta_eval}
	We have
	\begin{equation}
		\label{eq:inline_wi_lemma}
		h(x_j) = \left(\firstgreens_j, \Delta h\right)_{L^2(\Omega)} + \avg(h)
	\end{equation}
	for all $h\in H^2_N(\Omega)$, where
	\begin{equation*}
		\avg(h) :=	 \frac{1}{|\Omega|} \int_\Omega h ~dx,
	\end{equation*}
	and $|\Omega| = \int_\Omega 1 ~dx$ is the Lebesgue measure of $\Omega$.
\end{lem}

@@

\begin{lem}[Characterization of $\pointinteractionmatrix$]
	\label{lem:S_matrix_characterizations}
	We have
	\begin{equation*}
		\pointinteractionmatrix_{ij} = \secondgreens_j(x_i).
	\end{equation*}
\end{lem}

\begin{proof}
	We compute
	\begin{equation*}
		\secondgreens_j(x_i) = \left(\firstgreens_i, \Delta \secondgreens_j\right)_{L^2(\Omega)} + \avg\left(\secondgreens_j\right)
		= \left(\firstgreens_i, \firstgreens_j\right)_{L^2(\Omega)} = \pointinteractionmatrix_{ij}.
	\end{equation*}
	In the first equality we used Lemma \ref{lem:psi_delta_eval}. In the second equality we used the facts that $\Delta \secondgreens_j = \firstgreens_j$ and $\avg(\secondgreens_j) = \left(1 / |\Omega|\right) \int_\Omega \secondgreens_j = 0$ from the definition of $\secondgreens_j$ in \eqref{eq:theta_eq}. 
\end{proof}

@@

	\paragraph{Feasibility} To show that $v_*$ is feasible (i.e., $v_* \in X$), we must show that $v_* \in H^2_N(\Omega)$ and $v_*(x_i) = \interpolatedvalues_i$ for $i=1,\dots,\convrank$. We already showed that $v_* \in H^2_N(\Omega)$ in Theorem \ref{thm:wi_no_breakdown}. Using the the definition of $v_*$ in \eqref{eq:optimal_v} and Lemma \ref{lem:S_matrix_characterizations}, we have
	\begin{equation*}
		v_*(x_i) = \constcoeff + \sum_{j=1}^\convrank \secondgreenscoeff_j \secondgreens_j(x_i)
		= \constcoeff + \sum_{j=1}^\convrank \secondgreenscoeff_j \pointinteractionmatrix_{ij} = \left(\pointinteractionmatrix \bm{\secondgreenscoeff} + \constcoeff \bm{1}\right)_i.
	\end{equation*}
	The conditions $v_*(x_i) = \interpolatedvalues_i$ for $i=1,\dots,\convrank$ may therefore be written in matrix form as
	$
		\pointinteractionmatrix \bm{\secondgreenscoeff} + \constcoeff \bm{1} = \bm{\interpolatedvalues}
	$, and this matrix equation must hold because it is the first block row of system \eqref{eq:interpolation_linear_system} which is solved to compute $\bm{\secondgreenscoeff}$ and $\constcoeff$. So $v_* \in X$.
